---ogram
title: "test2"
output: html_document
date: '2022-07-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
la1<-read.csv(file.choose(),header=TRUE)
la1
```
chapter 2.
1.scatter plot
```{r}
plot(la1$Total.Cases,la1$Total.Deaths)
```

2.line graph
```{r}
library(ggplot2)
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) +
geom_line()
```
3.bar graph
```{r}
ggplot(la1, aes(x = Total.Deaths, y = Total.Cases)) +
geom_col()
```
4.bar graph of counts
```{r}
ggplot(la1, aes(x = factor(Total.Deaths))) +
geom_bar()
```
5. making a histogram
```{r}
u1<-la1$Total.Deaths[1:10]
u1
hist(u1, breaks = 10)
```
6.histogram with  bin
```{r}
ggplot(la1, aes(x = Total.Deaths)) +
geom_histogram(binwidth =3)
```
7.boxplot
```{r}
boxplot(Total.Cases ~ Total.Deaths , data = la1)
```
8.function curve
```{r}
curve(x^3 - 5*x, from = -4, to = 4)
```
9.box plot for multiple variables by combining the variables with interaction
```{r}
ggplot(la1, aes(x = interaction(Total.Cases, Total.Deaths), y = Total.Tests)) +
geom_boxplot()
```
10.bar plot of values
```{r}
barplot(la1$Total.Cases, names.arg = la1$State)
```
11.making a basic bar graph
```{r}
ggplot(la1, aes(x = Total.Deaths, y = Active.Cases)) +
geom_col()
```
12.converting continuous variable to discrete variable
```{r}
ggplot(la1, aes(x = factor(Total.Cases), y = Total.Deaths)) +
geom_col()
```
13.adding color to bar graph
```{r}
ggplot(la1, aes(x = Total.Deaths, y = Active.Cases)) +
geom_col(fill = "lightpink", colour = "red")
```
14.grouping bars together by a second variable
```{r}
ggplot(la1, aes(x = Total.Deaths, y =Total.Cases, fill = Total.Tests)) +
geom_col(position = "dodge")
```
15.adding outline and color palette to grouped bars
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Recovered, fill = State)) +
geom_col(position = "dodge", colour = "black") +
scale_fill_brewer(palette = "Pastel1")
```
16.graph with a missing bar
```{r}
library(ggplot2)
ce <-la1[1:5]
ggplot(ce, aes(x = factor(Total.Cases),y=Total.Recovered, fill = State)) +
geom_col(position = "dodge", colour = "black") +
scale_fill_brewer(palette = "Pastel1")
```
17.making bar graph of counts
```{r}
ggplot(la1, aes(x = Total.Deaths)) +
geom_bar()
```
18.bar graph of counts on a continuous axis
```{r}
ggplot(la1, aes(x = Total.Deaths)) +
geom_bar(stat= "bin")
```
19.adding color to bars using arrange
```{r}
library(dplyr)
trial <- la1 %>%
arrange(desc(Total.Deaths)) %>%
slice(1:10)
ggplot(trial, aes(x = Total.Cases, y = Total.Deaths, fill = State)) +
geom_col()
```
20.stacked bar graph
```{r}
ggplot(la1, aes(x = Total.Deaths, y = Total.Cases, fill = State)) +
geom_col()
```
chp-4 line graph

21.Basic line graph with a factor on the x-axis. When the x variable is a factor, you must also use aes(group=1) to ensure that ggplot knows that the data points belong together and should be connected with a line
```{r}
la3 <- la1 # Make a copy of the data
la3$Total.Cases <- factor(la3$Total.Cases)
ggplot(la3, aes(x = Total.Cases, y = Total.Deaths, group = 1)) +
geom_line()
```
22.Line graph with manually set y range.
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) + geom_line() + expand_limits(y = 0)
```
23.Adding Points to a Line Graph
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) +geom_line() +geom_point()
```
24.log y axis - Sometimes it is useful to indicate each data point on a line graph. This is helpful when the density of observations is low, or when the
observations do not happen at regular intervals.
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) + geom_line() + geom_point() + scale_y_log10()
```
25.Making a Line Graph with Multiple Lines.In addition to the variables mapped to the x- and y-axes, map another (discrete) variable
to colour or linetype,as shown below.
```{r}
# Map state to colour
ggplot(la1, aes(x = Total.Deaths, y = Active.Cases, colour = State)) +
geom_line()
# Map state to linetype
ggplot(la1, aes(x = Total.Deaths, y = Active.Cases, linetype = State)) +
geom_line()
```
26.Changing the Appearance of Lines
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) + geom_line(linetype = "dashed", size = 1, colour = "blue")
```
27.change the appearance of the points in a line graph.- In geom_point(), set the size, shape, colour, and/or fill outside of aes()
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) + geom_line() + geom_point(size = 4, shape = 22, colour = "darkred", fill = "pink")
```
28.Making a Graph with a Shaded Area -Use geom_area() to get a shaded area,
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) + geom_area()
```
29.Making a Stacked Area Graph- Use geom_area() and map a factor to fill
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths, fill = factor(Total.Tests))) + geom_area()
```
30.Adding a Confidence Region - Use geom_ribbon() and map values to ymin and ymax.
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) +geom_ribbon(aes(ymin = Total.Recovered - Total.Deaths, ymax = Total.Deaths + Total.Recovered),alpha = 0.2) +geom_line()
```
chp-5 scatterplots
31.Making a Basic Scatter Plot
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) +geom_point()
```
32.Grouping Points Together Using Shapes or Colors - we want to visually group points by some variable (the grouping variable), using different
shapes or colors.
```{r}
library(dplyr)
trial<- la1 %>%select(Total.Cases, Total.Deaths, Total.Recovered)
ggplot(trial, aes(x = Total.Cases, y = Total.Recovered, shape = factor(Total.Deaths), colour = factor(Total.Deaths))) + geom_point()
```
33.Using Different Point Shapes- You want to change the default scatter plot shapes for the data points.You can set the shape of all the data points at once by setting a shape in geom_point(): 
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) + geom_point(shape = 3)
```
34.Mapping a Continuous Variable to Color or Size-You want to represent a third continuous variable using color.
```{r}
ggplot(la_mod, aes(x = Total.Recovered, y = Total.Cases, colour = Total.Deaths)) +geom_point()
```
35.data with discrete x variable 
```{r}
cw_sp <- ggplot(la1, aes(x = Total.Cases, y = Total.Recovered))
cw_sp +geom_point()
cw_sp +geom_point(position = "jitter") # Equivalent to using geom_jitter()
cw_sp +geom_point(position = position_jitter(width = .5, height = 0))
```
36.Adding Fitted Regression Model Lines
```{r}
cw_sp +geom_point() +stat_smooth(method = lm)
```
37.LOESS (locally weighted polynomial) curve
```{r}
cw_sp + geom_point(colour = "grey60") +stat_smooth(method = loess)
``` 
38.Adding marginal rugs to a scatter plot
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Deaths)) +geom_point() +geom_rug()
```
39.Labeling Points in a Scatter Plot
```{r}
usa_sp <- ggplot(la3, aes(x = Total.Cases, y = Total.Deaths)) +geom_point()
usa_sp +geom_text(aes(label = State), size = 4)
```
40.balloon plot
```{r}
cdat_sp <- ggplot(la3, aes(x = Total.Cases, y = Total.Recovered, size = Total.Deaths)) +geom_point(shape = 21, colour = "black", fill = "cornsilk")
cdat_sp
```
chp-6 summarizing data
41.Making Multiple Histograms from Grouped Data
```{r}
ggplot(la2, aes(x = Total.Cases)) + geom_histogram(fill = "white", colour = "black") +facet_grid(State ~ .)
```
42.multiple histogram with different fill colors
```{r}
ggplot(la2, aes(x = Total.Cases, fill = State)) +geom_histogram(position = "identity", alpha = 0.4)
```
43.Density curve
```{r}
ggplot(la1, aes(x = Total.Cases)) +geom_density()
```
44.Making Multiple Density Curves from Grouped Data
```{r}
ggplot(la1, aes(x = Total.Cases, fill = Total.Deaths)) +geom_density(alpha = .3)
```
45.Making a Frequency Polygon= make a frequency polygon
```{r}
ggplot(la1, aes(x=Total.Cases)) + geom_freqpoly()
```
46.Adding notches to a box plot
```{r}
ggplot( la1,aes(x = factor(State), y = Total.Recovered)) +geom_boxplot(notch = TRUE)
```
47.Making a Violin Plot
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Recovered, size = Total.Deaths))+geom_violin()
```
48.Wilkinson dotplot
```{r}
library(dplyr)
c2009 <- la1 %>% filter(Total.Deaths > 20000)
c2009_p <- ggplot(c2009, aes(x = Total.Deaths))
c2009_p +geom_dotplot()
```
49.Making Multiple Dot Plots for Grouped Data
```{r}
ggplot(la1, aes(x = Total.Cases, y = Total.Recovered)) +geom_dotplot(binaxis = "y", binwidth = .5, stackdir = "center")
```
